Spectral partitioning identifies individual heterogeneity in the functional network topography of ventral and anterior medial prefrontal

### 2019-09-14 Manuscript.Rmd
yet more tweaks

# stats: one sample t's per hemisphere/region
curvStats <- curvCors %>% 
                group_by(region, Hemisphere) %>% 
                summarise(meanCor = mean(Correlation),
                          seCor = sd(Correlation) / sqrt(nSubj),
                          TStat = round(t.test(Correlation)$statistic, digits = 2),
                          p_unc = t.test(Correlation)$p.val,
                          Sig = p < 0.05,
                          ES = DescTools::CohenD(Correlation))

# FDR correction
curvStats$p <- round(p.adjust(curvStats$p_unc, method = "BY"), digits = 3)

@@

We quantified these observations by dividing the search space into three regions: a ventral mPFC area corresponding to the region tested by Lopez-Persem et al. [-@Lopez2019], a superior mPFC area (sup-mPFC) that contained the remaining mPFC regions, and PCC (Figure 8B, left). For each individual, we correlated the unthresholded Fiedler vector with cortical curvature for each combination of region and hemisphere. Negative correlations in this context imply that the DN was found in sulci and non-DN in gyri. Results are shown in Figure 8B. Correlations tended to be slightly negative in vmPFC, both on the left (mean correlation = `r round(curvStats$meanCor[5], digits = 2)`, SE = `r round(curvStats$seCor[5], digits = 2)`) and right (mean correlation = `r round(curvStats$meanCor[6], digits = 2)`, SE = `r round(curvStats$seCor[6], digits = 2)`); the distribution was only significantly different from zero in the right hemisphere, and weakly so (one sample t-test: t = `r curvStats$TStat[6]`, *p* `r ifelse(curvStats$p[6] < 0.001, "< 0.001", paste("=", curvStats$p[6]))`, FDR corrected; Cohen's D = `r round(curvStats$ES[6], digits = 2)`). Correlations between FV and curvature were positive and significantly different from zero in sup-mPFC, both on the left (mean correlation = `r round(curvStats$meanCor[3], digits = 2)`, SE = `r round(curvStats$seCor[3], digits = 2)`; one sample t-test: t = `r curvStats$TStat[3]`, *p* `r ifelse(curvStats$p[3] < 0.001, "< 0.001", paste("=", curvStats$p[3]))`; Cohen's D = `r round(curvStats$ES[3], digits = 2)`) and right (mean correlation = `r round(curvStats$meanCor[4], digits = 2)`, SE = `r round(curvStats$seCor[4], digits = 2)`; one sample t-test: t = `r curvStats$TStat[4]`, *p* `r ifelse(curvStats$p[4] < 0.001, "< 0.001", paste("=", curvStats$p[4]))`; Cohen's D = `r round(curvStats$ES[4], digits = 2)`). Correlations in PCC were negative and significantly different from zero in the left hemisphere (mean correlation = `r round(curvStats$meanCor[1], digits = 2)`, SE = `r round(curvStats$seCor[1], digits = 2)`; one sample t-test: t = `r curvStats$TStat[1]`, *p* `r ifelse(curvStats$p[1] < 0.001, "< 0.001", paste("=", curvStats$p[1]))`; Cohen's D = `r round(curvStats$ES[1], digits = 2)`), but significantly above zero in the right hemisphere (mean correlation = `r round(curvStats$meanCor[2], digits = 2)`, SE = `r round(curvStats$seCor[2], digits = 2)`; one sample t-test: t = `r curvStats$TStat[2]`, *p* `r ifelse(curvStats$p[2] < 0.001, "< 0.001", paste("=", curvStats$p[2]))`; Cohen's D = `r round(curvStats$ES[2], digits = 2)`). The difference across hemispheres was significant (paired t-test: t = `r round(curvPCC_t$statistic, digits = 2)`, *p* `r ifelse(curvPCC_t$p.val < 0.001, "< 0.001", paste("=", curvPCC_t$p.val))`; Cohen's D = `r round(curvPCC_ES, digits = 2)`). These results provide preliminary indictations that the association between function and structure is heterogenous across subregions of the canonical DN.

>>>>

# stats: one sample t's per hemisphere/region
curvStats <- curvCors %>% 
                group_by(region, Hemisphere) %>% 
                summarise(meanCor = mean(Correlation),
                          seCor = sd(Correlation) / sqrt(nSubj),
                          TStat = round(t.test(Correlation)$statistic, digits = 2),
                          p = round(t.test(Correlation)$p.val, digits = 3),
                          Sig = p < 0.05,
                          ES = DescTools::CohenD(Correlation))

@@

We quantified these observations by dividing the search space into three regions: a ventral mPFC area corresponding to the region tested by Lopez-Persem et al. [-@Lopez2019], a superior mPFC area (sup-mPFC) that contained the remaining mPFC regions, and PCC (Figure 8B, left). For each individual, we correlated the unthresholded Fiedler vector with cortical curvature for each combination of region and hemisphere. Negative correlations in this context imply that the DN was found in sulci and non-DN in gyri. Results are shown in Figure 8B. Correlations tended to be slightly negative in vmPFC, both on the left (mean correlation = `r round(curvStats$meanCor[5], digits = 2)`, SE = `r round(curvStats$seCor[5], digits = 2)`) and right (mean correlation = `r round(curvStats$meanCor[6], digits = 2)`, SE = `r round(curvStats$seCor[6], digits = 2)`); the distribution was only significantly different from zero in the right hemisphere, and weakly so (one sample t-test: t = `r curvStats$TStat[6]`, *p* `r ifelse(curvStats$p[6] < 0.001, "< 0.001", paste("=", curvStats$p[6]))`; Cohen's D = `r round(curvStats$ES[6], digits = 2)`). Correlations between FV and curvature were positive and significantly different from zero in sup-mPFC, both on the left (mean correlation = `r round(curvStats$meanCor[3], digits = 2)`, SE = `r round(curvStats$seCor[3], digits = 2)`; one sample t-test: t = `r curvStats$TStat[3]`, *p* `r ifelse(curvStats$p[3] < 0.001, "< 0.001", paste("=", curvStats$p[3]))`; Cohen's D = `r round(curvStats$ES[3], digits = 2)`) and right (mean correlation = `r round(curvStats$meanCor[4], digits = 2)`, SE = `r round(curvStats$seCor[4], digits = 2)`; one sample t-test: t = `r curvStats$TStat[4]`, *p* `r ifelse(curvStats$p[4] < 0.001, "< 0.001", paste("=", curvStats$p[4]))`; Cohen's D = `r round(curvStats$ES[4], digits = 2)`). Correlations in PCC were negative and significantly different from zero in the left hemisphere (mean correlation = `r round(curvStats$meanCor[1], digits = 2)`, SE = `r round(curvStats$seCor[1], digits = 2)`; one sample t-test: t = `r curvStats$TStat[1]`, *p* `r ifelse(curvStats$p[1] < 0.001, "< 0.001", paste("=", curvStats$p[1]))`; Cohen's D = `r round(curvStats$ES[1], digits = 2)`), but significantly above zero in the right hemisphere (mean correlation = `r round(curvStats$meanCor[2], digits = 2)`, SE = `r round(curvStats$seCor[2], digits = 2)`; one sample t-test: t = `r curvStats$TStat[2]`, *p* `r ifelse(curvStats$p[2] < 0.001, "< 0.001", paste("=", curvStats$p[2]))`; Cohen's D = `r round(curvStats$ES[2], digits = 2)`). The difference across hemispheres was significant (paired t-test: t = `r round(curvPCC_t$statistic, digits = 2)`, *p* `r ifelse(curvPCC_t$p.val < 0.001, "< 0.001", paste("=", curvPCC_t$p.val))`; Cohen's D = `r round(curvPCC_ES, digits = 2)`). These results provide preliminary indicatations that the association between function and structure is heterogenous across subregions of the canonical DN.
